### 2020-06-03 report/sections/general/p2p/challenges.tex
Report: add citation to chapter 7

Existing work in decomposing multiparty sessions into a collection
of binary sessions do resemble our routing proposal, but their approach
involves having an endpoint to exclusively carry out
routing responsibilities and act as a centralised orchestrator 
for the multiparty session.
Our proposal recognises that, in the context of web applications,
there is a need for server-side endpoints to implement business logic
so enforcing the server to be an exclusive orchestrator makes our work
incompatible with webservice protocols; 
we also argue that the server can still participate in the 
multiparty session and concurrently perform its routing duties
in a way that is transparent to non-server endpoints, and crucially,
does not overserialise the permitted interactions. 
We introduce our extension as \textit{Routed Session Types},
and proceed to prove these claims in \cref{chap:theory}.

>>>>

There is existing work \cite{LinearDecomp, BinaryDecomp, BinaryDuality}
that resembles our routing proposal through
\textit{decomposing} multiparty sessions into a collection
of binary sessions,
but these approaches
specify an endpoint to exclusively carry out
routing responsibilities and act as a centralised orchestrator 
for the multiparty session.
Our proposal recognises that, in the context of web applications,
there is a need for server-side endpoints to implement business logic
so enforcing the server to be an exclusive orchestrator makes our work
incompatible with webservice protocols; 
we also argue that the server can still participate in the 
multiparty session and concurrently perform its routing duties
in a way that is transparent to non-server endpoints, and crucially,
does not overserialise the permitted interactions. 
We introduce our extension as \textit{Routed Session Types},
and proceed to prove these claims in \cref{chap:theory}.
